The problem and promise of scale in multilayer animal social networks

### 2020-02-12 paper/manuscript.Rmd
related to

Contrasting winter and summer seasons became more similar with increasing window
length. Individual graph strength and layer relevance increased for all summer
layers as individuals became more connected with increasing window lengths
(Figure \@ref(fig:winlen)a, Figure \@ref(fig:winlen)b). Layer similarity between
seasons increased consistently across landcover class (Figure
\@ref(fig:winlen)b).  These results suggest that an increasing window length,
especially for the summer season, may be resulting in less precisely defined
seasons that are not clearly capturing periods of aggregation and
dissaggregation according to resource availability and presence of conspecifics.

>>>>

Contrasting winter and summer seasons became more similar with increasing window
length. Individual graph strength and layer relevance increased for all summer
layers as individuals became more connected with increasing window lengths
(Figure \@ref(fig:winlen)a, Figure \@ref(fig:winlen)b). Layer similarity between
seasons increased consistently across landcover class (Figure
\@ref(fig:winlen)b).  These results suggest that an increasing window length,
especially for the summer season, may be resulting in less precisely defined
seasons that are not clearly capturing periods of aggregation and
dissaggregation related to resource availability.
